\documentations[11pt,a4paper,sans]{resume}

% ModernCV themes
\moderncvstyle{banking}
\moderncvcolor{black}

\usepackage[utf8]{inputenc}
\usepackage[scale=0.85]{geometry}
\usepackage{import}
\usepackage{wasysym}

% Personal Data
\name{Handsome}{Mofokeng}
\title{Mobile Developer (Kotlin \& Jetpack Compose Specialist)}
\address{Johannesburg, Gauteng}{South Africa}
\phone[mobile]{0632881025}
\email{handsomem23@hotmail.com}
\social[linkedin]{handsome-mofokeng}
% \photo[64pt][0.4pt]{picture} % Optional picture

% Content
\begin{document}

\makecvtitle

\section{Professional Profile}\label{sec:professional-profile}
I am a dedicated \textbf{Mobile Development specialist}, with expertise anchored in \textbf{Native Android}, Kotlin, and the modern Jetpack Compose framework. My core focus is delivering high-quality, high-performance mobile applications. I manage the full Software Development Lifecycle (SDLC), employing robust practices like MVVM architecture and Test-Driven Development (TDD) to ensure stability from conceptualization to Play Store deployment.

\section{Technical Skills}\label{sec:technical-skills}
\begin{itemize}
    \item \textbf{Android Core:} Kotlin (Primary), Jetpack Compose, Android SDK \& Native, AAC \& MVVM
    \item \textbf{Quality \& DevOps:} Unit Testing \& TDD, Gitlab CI/CD, Google Play Console, Debugging \& Standards
    \item \textbf{Languages:} Kotlin \& Java, Dart (Flutter), Swift (Exposure), XML
    \item \textbf{Methodology:} Agile \& Scrum, SDLC Management, Technical Specs, Jira Workflows
\end{itemize}

\section{Experience}\label{sec:experience}

\cventry{2022/08 -- Present}{Mobile Developer}{Standard Bank}{Finance}{}{
\begin{itemize}
    \item Develop, test, and deploy enterprise-level mobile applications using Kotlin.
    \item Design modern UI/UX using Jetpack Compose for enhanced user engagement.
    \item Implement rigorous Unit Testing and professional coding standards.
    \item Manage CI/CD pipelines via Gitlab for frequent internal and production releases.
    \item Proactively communicate workload and timelines to business stakeholders.
\end{itemize}
}

\cventry{2021/06 -- 2022/07}{Mobile Developer}{Acumen Software}{IT \& Telecommunications}{}{
\begin{itemize}
    \item Enhanced existing applications and developed new customer-facing apps.
    \item Analyzed requirements and created technical specifications.
    \item Provided technical guidance to team members and mentored juniors.
    \item Monitored and corrected software defects in production environments.
\end{itemize}
}

\cventry{2019/02 -- 2021/05}{Developer}{Dimension Data}{IT \& Telecommunications}{}{
\begin{itemize}
    \item Focused on software development, analysis, and modification.
    \item Provided technical mentorship and ensured code quality.
    \item Assisted with SharePoint Administration and server health automation.
    \item Gained experience in Managed Services and IT Support.
\end{itemize}
}

\section{Key Projects}\label{sec:key-projects}
\cvitem{ComposeWhatsApp}{A clone of the WhatsApp UI built entirely with Jetpack Compose, demonstrating advanced UI capabilities and modern Android architecture. (Kotlin)}
\cvitem{Standard Bank App}{Enterprise financial application. Contributed to core banking features, UI modernization, and stability improvements. (Kotlin)}
\cvitem{MySmart.City App}{A citizen engagement platform allowing users to report issues and interact with city services. (Java Native, Android, Flutter/Dart)}
\cvitem{SRC Voting App}{A secure voting application designed for Student Representative Council elections. Re-implemented as a Flutter/Dart concept project. (Flutter)}

\section{Education}\label{sec:education}
\cventry{2015 -- 2018}{N. Diploma IT (Software Development)}{Central University of Technology}{}{}{}
\cventry{2013 -- 2014}{BSc IT (Bridging Program)}{University of Free State}{}{}{}
\cventry{2009 -- 2011}{National Senior Certificate (Matric)}{Mampoi High School}{}{}{}

\end{document}
